Concentration Inequalities

### 2015-09-30 causal-bandit/observe_then_best.tex
updates algorithm description for simple regret

\begin{algorithm}[H]
\caption{Simple Regret Algorithm}\label{alg:simple}
\begin{algorithmic}[1]
\State {\bf Input:} $T, N$
\State $h = T/2$
\For{$t \in 1,\ldots,h$}
\State Do nothing and observe $X_{i,t}$ for $i \in \set{1,\ldots,N}$ and $r_t$
\EndFor
\State Compute $\hat q_i = \frac{1}{h} \sum_{t=1}^n X_{i,t}$
\State Compute $\hat s_i = \min\set{\hat q_i, 1 - \hat q_i}$
\State Compute $\hat m = \min\set{2 \leq i \leq N : \hat s_{(i)} \geq 1/i}$
\State Compute $A$ is subset of insufficiently explored arms with $|A| = \hat m$
\State Compute for all $i \in \set{1,\ldots,N}$ and $j \in \set{0,1}$:
\eq{
\hat \mu_{i,j} = \frac{\sum_{t=1}^h \ind{X_i = j} r_t}{\sum_{t=1}^h \ind{X_i = j}}\,.
}
\For{$i \in A$}
\State $j = \ind{\hat q_{I_t} \geq 1/2}$
\For{$t \in 1,\ldots,h/\hat m$}
\State Choose $I = i$ and $J = j$
\State Observe reward $r_t$
\EndFor
\State Recompute $\hat \mu_{i,j} = \frac{\hat m}{h} \sum_{t=1}^{\hat m/h} r_t$ 
\EndFor
\end{algorithmic}
\end{algorithm}

\begin{theorem}\label{thm:simple-regret}
Define $m = \min\set{i : q_i \geq 1/i}$.
Then the algorithm given in \cref{alg:simple} satisfies
\eq{
r_q(T) \in O\left(\sqrt{\frac{m}{T} \log \left(\frac{NT}{m}\right)}\right)\,.
}
\end{theorem}

@@

\begin{proof}[Proof of \cref{thm:simple-regret}]
Given the assumption that
\eq{
h \geq 12m \log \frac{N}{\delta}
}
we have shown with probability at least $1 - \delta$ that
\eq{
(\forall i, j) \qquad \left|\hat \mu_{i,j} - \mu_{i,j}\right| \leq \sqrt{\frac{m}{h} \log\frac{N}{\delta}}\,.
}
Suppose $h < 12m \log \frac{N}{\delta}$. Then
\eq{
\left|\hat \mu_{i,j} - \mu_{i,j}\right| \leq 1 \leq \sqrt{\frac{12m}{h} \log \frac{N}{\delta}}\,.
}
Therefore
\eq{
\left|\hat \mu_{i,j} - \mu_{i,j}\right| \leq \sqrt{\frac{12m}{h} \log \frac{N}{\delta}}\,.
}
Therefore 
\eq{
r_q(T) 
&\leq \delta + \sqrt{\frac{12m}{h} \log \frac{N}{\delta}} \\
&= \delta + \sqrt{\frac{24m}{T} \log \frac{N}{\delta}} \\
&\leq \frac{m}{T} + \sqrt{\frac{24m}{T} \log \left(\frac{NT}{m}\right)}
}
as required.
\end{proof}

@@

Let $D = \sqrt{\frac{8}{h}\log(hk)}$

\eqn{
R_2 \leq (T-h)\left(\sqrt{\frac{8}{h}\log(hk)} + \frac{1}{h}\right)
}

@@

\eqn{
R_T & \leq \frac{h}{K}\sum_i \Delta_i + (T-h)\left(\sqrt{\frac{8}{h}\log(hk)} + \frac{1}{h}\right)\\
& \leq h + T\left(\sqrt{\frac{8}{h}\log(Tk)} + \frac{1}{h}\right)
}

>>>>

\begin{algorithm}[H]
\caption{Simple Regret Algorithm}\label{alg:simple}
\begin{algorithmic}[1]
\State {\bf Input:} $T, N$
\State $h = T/2$
\For{$t \in 1,\ldots,h$}
\State Do nothing and observe $X_{i,t}$ for $i \in \set{1,\ldots,N}$ and $r_t$
\EndFor
\State Compute for all $i \in \set{1,\ldots,N}$ and $j \in \set{0,1}$:
\eq{
\hat \mu_{i,j} = \frac{\sum_{t=1}^h \ind{X_i = j} r_t}{\sum_{t=1}^h \ind{X_i = j}}\,.
}
\State Compute $\hat q_i = \frac{1}{h} \sum_{t=1}^h X_{i,t}$
\State Compute $\hat s_i = \min\set{\hat q_i, 1 - \hat q_i}$
\State Compute $\hat{s'} = sorted(\hat{s}) : \hat{s'}_1 \leq \hat{s'_2} \leq ... \leq \hat{s'}_N$
\State Compute $\hat m = \min\set{2 \leq i \leq N : \hat s'_{i} \geq 1/i}$
\State $i'(i) = $ the index of $\hat s_i$ in $\hat s'$
\State Compute $A$ as the subset of infrequently observed arms $\{(i,j):i'(i) \leq \hat m, j = \ind{\hat q_{i} \leq \frac{1}{2}} \}$ with $|A| = \hat m$

\For{$(i,j) \in A$}
\For{$t \in 1,\ldots,h/\hat m$}
\State Choose $I = i$ and $J = j$
\State Observe reward $r_t$
\EndFor
\State Recompute $\hat \mu_{i,j} = \frac{\hat m}{h} \sum_{t=1}^{\hat m/h} r_t$ 
\EndFor
\end{algorithmic}
\end{algorithm}

\begin{theorem}\label{thm:simple-regret}
Define $m = \min\set{2 \leq i \leq N : q_i \geq 1/i}$.
Then the algorithm given in \cref{alg:simple} satisfies
\eq{
r_q(T) \in O\left(\sqrt{\frac{m}{T} \log \left(\frac{NT}{m}\right)}\right)\,.
}
\end{theorem}

@@

\begin{proof}[Proof of \cref{thm:simple-regret}]
Given the assumption that
\eq{
h \geq 12m \log \frac{N}{\delta}
}

\eq {
\text{ for } (i,j)\in A \qquad \hat \mu_{i,j} = \frac{\hat m}{h} \sum_{t=1}^{\hat m/h} r_t
}
Prove bound for this case

\eq {
\text{ for } (i,j)\notin A \qquad \hat \mu_{i,j} = \frac{\sum_{t=1}^h \ind{X_i = j} r_t}{\sum_{t=1}^h \ind{X_i = j}}
}

Prove bound for this case

we have shown with probability at least $1 - \delta$ that
\eq{
(\forall i, j) \qquad \left|\hat \mu_{i,j} - \mu_{i,j}\right| \leq \sqrt{\frac{m}{h} \log\frac{N}{\delta}}\,.
}
Suppose $h < 12m \log \frac{N}{\delta}$. Then
\eq{
\left|\hat \mu_{i,j} - \mu_{i,j}\right| \leq 1 \leq \sqrt{\frac{12m}{h} \log \frac{N}{\delta}}\,.
}
Therefore
\eq{
\left|\hat \mu_{i,j} - \mu_{i,j}\right| \leq \sqrt{\frac{12m}{h} \log \frac{N}{\delta}}\,.
}
Therefore 
\eq{
r_q(T) 
&\leq \delta + \sqrt{\frac{12m}{h} \log \frac{N}{\delta}} \\
&= \delta + \sqrt{\frac{24m}{T} \log \frac{N}{\delta}} \\
&\leq \frac{m}{T} + \sqrt{\frac{24m}{T} \log \left(\frac{NT}{m}\right)}
}
as required.
\end{proof}

@@

Let $D = \sqrt{\frac{8}{h}\log(hK)}$

\eqn{
R_2 \leq (T-h)\left(\sqrt{\frac{8}{h}\log(hK)} + \frac{1}{h}\right)
}

@@

\eqn{
R_T & \leq \frac{h}{K}\sum_i \Delta_i + (T-h)\left(\sqrt{\frac{8}{h}\log(hK)} + \frac{1}{h}\right)\\
& \leq h + T\left(\sqrt{\frac{8}{h}\log(TK)} + \frac{1}{h}\right)
}
